R Script V5

### 2023-05-27 Data & Scripts/MSC R Script.Rmd
OE3C Presentation
Amended files for the OE3C Presentation

```{r Open Crow and manage, include =F}
setwd(getwd())
Crow<-read.csv("Crow.csv", stringsAsFactors = T)
#Some management #
Crow$ID<-as.factor(Crow$ID)
Crow$Number.of.Crows<-as.numeric(Crow$Number.of.Crows)
Crow$CODED_BAIT<-as.numeric(Crow$CODED_BAIT)
Crow$CODED_G.ENV<-as.numeric(Crow$CODED_G.ENV)
Crow$CODED_NB_CROWS<-as.numeric(Crow$CODED_NB_CROWS)
Crow$CODED_SENTINEL<-as.numeric(Crow$CODED_SENTINEL)
Crow$CODED_BEHAVIOR<-as.numeric(Crow$CODED_BEHAVIOR)
Crow$LDur<-log(Crow$Duration+1)
```

@@

```{r Dot Plot V2, echo = F}
source("./Calculate Summary Table with SE, SD, CI by grouping variables.R")
MeanDur <- summarySE(data = Crow, measurevar = "Duration"
                     , groupvars = c("G.Env", "Behavior", "Sentinel"))
DurDot<-ggplot(data = MeanDur
               , aes(x = G.Env
                     , y = Duration
                     , color = Behavior
                     , shape = Sentinel))+
  geom_point(position = position_dodge2(width = 0.9)
             , size = 3) +
  geom_errorbar(aes(ymin=(Duration-se)
                    , ymax=(Duration+se))
                , width = 0.2
                , position = position_dodge(width=0.9))+
  theme_bw() +
  ylab("Mean Bout Duration (s)") +
  scale_colour_manual(values = cbPalette
                      , labels = c("Foraging", "Alert", "Moving")) +
  scale_shape_manual(values = c(16,17)
                     , labels = c("Sentinel Absent"
                                  , "Sentinel Present")) +
  theme(axis.title.x = element_blank()
        , legend.position = "bottom"
        , legend.box="vertical"
        , legend.margin=margin())

@@

### PCAs
```{r Bout Duration PCA packages, include=F}
library("FactoMineR")
library("factoextra")
```
```{r Bout Duration PCA Book keeping, include=F}
PCA.Crow.Data<-Crow[,c(4,6,8,10,12:13)]
head(PCA.Crow.Data)
```
```{r Bout Duration PCA, echo=F}
PCA.Crow<-PCA(PCA.Crow.Data[,-5], ncp=5)
```

>I'm new to PCAs, so bear with me please. From what I see, presence of bait and sentinel, and the number of crows all contibute to PC1, while Generalized environment seems to be contributing to PC2. The behavior appears to contribute to PC2, but not a lot.

#### Eigenvalues

>Let's have a look at the eigenvalues.

``` {r Bout Duration PCA eigenvalues, echo = F}
Crow.eig.val<-get_eigenvalue(PCA.Crow)
Crow.eig.val
```

>Pretty small values. The second column shows how much contribution each dimension has to explain the total variance in the data. Let's quickly plot that.

#### Scree Plot

```{r Bout Duration PCA Scree Plot, echo = F}
fviz_eig(PCA.Crow, addlabels=T, ylim = c(0,40))
```

>Pretty cool. The first 3 PCs explain ~77% of the variance. Adding the 4th PC explains ~93% of the variation.

#### Contribution of variables to Principal Components

```{r Bout Duration PCA var results, include = F}
Crow.var<-get_pca_var(PCA.Crow)
```
```{r Bout Duration PCA Contribution Dim 1, echo=F}
fviz_contrib(PCA.Crow, choice="var", axes = 1, top = 20)
```

>The red dotted line represents the expected average contribution, assuming the contribution of the variables were uniform. In other words, the line is equal to 1/the number of variables; in this case 1/5 or 20%.

> From this plot, I can see that, as I saw previously in the correlation circle, the number of crows, the presence of a sentinel and the presence of bait contribute the most to PC1 (Dimension 1)

```{r Bout Duration PCA Contribution Dim 2, echo=F}
fviz_contrib(PCA.Crow, choice="var", axes = 2, top = 20)
```

> The generalized environment contributes the most to PC2.

```{r Bout Duration PCA Contribution Dim 3, echo=F}
fviz_contrib(PCA.Crow, choice="var", axes = 3, top = 20)
```

>The coded behavior contributes most to PC3.

```{r Bout Duration PCA Contribution Dim 4, echo=F}
fviz_contrib(PCA.Crow, choice="var", axes = 4, top = 20)
```

>OK! Now we're getting to the interesting bits. The presence of bait and the presence of a Sentinel contribute most to PC4. This makes me curious to see if there is an interaction between the two factors.

```{r Bout Duration PCA Contribution Dim 5, echo=F}
fviz_contrib(PCA.Crow, choice="var", axes = 5, top = 20)
```

>>The presence of a sentinel and the size of the group contribute most to PC 5. I believe this would imply that the interaction between the two could be interesting to look at. Considering these two variables are also major contributors to PC1, this makes the inclusion of the interaction in the model a must.

>From this, I believe I should look at the interaction between NB_Crows, Presence of a sentinel, and the presence of bait.

#### Plotting with Behaviors

>I'd like to plot the dimensions using the behaviors of the bouts.

```{r Bout Duration PCA Plot with Behavior PC1-2, echo=F}
fviz_pca_ind(PCA.Crow
             , geom.ind="point"
             , col.ind=PCA.Crow.Data$Behavior
             , palette = cbPalette
             , addEllipses = T
             , legend.title = "Behaviors"
             )
```

>Messy. The mean points of the behaviors are relatively centered.

```{r Bout Duration PCA Plot with Behavior PC2-3, echo=F}
fviz_pca_ind(PCA.Crow
             , axes = c(2,3)
             , geom.ind="point"
             , col.ind=PCA.Crow.Data$Behavior
             , palette = cbPalette
             , addEllipses = T
             , legend.title = "Behaviors"
             )
```

>Very clear separation by behavior type, with 'Head Up' shifted upward, 'Head Down' shifted downward, and 'Moving' in the middle.

```{r Bout Duration PCA Plot with Behavior PC1-3, echo=F}
fviz_pca_ind(PCA.Crow
             , axes = c(1,3)
             , geom.ind="point"
             , col.ind=PCA.Crow.Data$Behavior
             , palette = cbPalette
             , addEllipses = T
             , legend.title = "Behaviors"
             )
```

>Good separation, but the concentration ellipses have increased in size. Curious.

#### Biplot

>Finally, let's look at the biplot. From what I understand, it is essentially the correlation circle overlaid onto the data.

```{r Bout Duration PCA Biplot PC1-2, echo=F}
fviz_pca_biplot(PCA.Crow
                ,geom.ind = "point"
                , repel = T
                , col.ind=PCA.Crow.Data$Behavior
                , addEllipses = T
                , label = "var"
                , palette=cbPalette
                , col.var="black"
                , legend.title = "Behavior")
```
```{r Bout Duration PCA Biplot PC2-3, echo=F}
fviz_pca_biplot(PCA.Crow
                , axes = c(2,3)
                , geom.ind = "point"
                , repel = T
                , col.ind=PCA.Crow.Data$Behavior
                , addEllipses = T
                , label = "var"
                , palette=cbPalette
                , col.var="black"
                , legend.title = "Behavior")
```
```{r Bout Duration PCA Biplot PC1-3, echo=F}
fviz_pca_biplot(PCA.Crow
                , axes = c(1,3)
                , geom.ind = "point"
                , repel = T
                , col.ind=PCA.Crow.Data$Behavior
                , addEllipses = T
                , label = "var"
                , palette=cbPalette
                , col.var="black"
                , legend.title = "Behavior")
```

>Nice! I think I've done the PCA analysis to the best of my abilities, but I am very much open to comments and feedback!

>From what I can gather, I should model the data as follows:/
>LDur~Behavior+NB_Crows*Bait*Sentinel+G.Env+(1|ID)

@@

```{r Duration RLMM, echo=F}
RLMM.Dur.I<-rlmer(LDur~Behavior+Sentinel*CODED_NB_CROWS*Baited+G.Env+ (1|ID), data = Crow)
plot(RLMM.Dur.I)
```

@@

```{r Duration Better Summary, echo = F}
sjPlot::tab_model(RLMM.Dur.I
                  , show.re.var = T
                  , title = "Model Results with Interactions"
                  , dv.labels = " Effects of on duration of behaviors")

@@

>Let's try the good old regular lmer and see if that changes anything.

@@

```{r Bait effect on HD bout, echo = F}
BaitPlot<- HD.Dur %>%
  summarySE(measurevar = "Duration"
            , groupvars = "Baited") %>%
  ggplot(aes(x = Baited, y = Duration))+
  geom_point(position = position_dodge(width = 0.9)
             , size = 3) +
  geom_text(aes(label = signif(Duration))
            , size = 3
            , position=position_dodge2(width=0.9, preserve='single')
            , hjust = -0.5
            , vjust = 0.1)+
  geom_errorbar(aes(ymin=(Duration-se), ymax=(Duration+se))
                , width = 0.2
                , position = position_dodge(width=.9))+
  theme_bw()+
  theme(text=element_text(size = 14))+
  xlab("Presence of Bait")+
  ylab("Mean Head Down Bout Duration (s)")+
  scale_x_discrete(labels=c("Not Baited", "Baited"))+
  theme(legend.position = 'bottom'
        )
BaitPlot
```

@@

```{r Proportion Barplot, echo = F}
Prop<-ggplot(MeanProp, aes(x = SENTINEL_PRESENCE, y = BEHAVIOR_PROPORTION, fill = BEHAVIOR))+
  geom_bar(stat = 'identity', position = 'stack')+
  geom_text(aes(label = paste0(signif(BEHAVIOR_PROPORTION*100), "%")), position = position_stack(vjust = 0.5)
            , size = 3)+
  scale_y_continuous(labels = scales::percent) +
  theme_bw()+
  theme(text=element_text(size = 10)
        , axis.title.x = element_blank())+
  ylab("Proportion of time")+
  scale_x_discrete(labels=c("Sentinel Absent", "Sentinel Present"))+
  scale_fill_manual(values = cbPalette, labels = c("Foraging", "Alert", "Moving"), name="Behavior")+
  theme(legend.position = "bottom")+
  facet_grid(~GENERALIZED_ENVIRONMENT)
Prop
```

@@

```{r Peck Per Minute Histograms Individual, include = F}
Untransformed.PPM<-hist(DATA$PECK_RATE, na.rm=T, breaks = 12)
Transformed.PPM<-hist(DATA$LPek, breaks = 12)
```

@@

```{r Peck Plots, echo = F}
PeckPlot<-ggplot(MeanPeck, aes(x = GENERALIZED_ENVIRONMENT, y = PECK_RATE, colour = SENTINEL_PRESENCE))+
  geom_point(position = position_dodge(width = 0.9)
             , size = 3)+
  geom_text(aes(label = signif(PECK_RATE))
            , size = 3
            , position=position_dodge2(width=1, preserve='single')
            , hjust = -0.5
            , vjust = 0.1)+
  geom_errorbar(aes(ymin=(PECK_RATE-se), ymax=(PECK_RATE+se))
                , width = 0.2
                , position = position_dodge(.9))+
  theme_bw()+
  labs(colour = "Presence of a sentinel")+
  ylab("Mean pecks per minute")+
  scale_color_manual(values = cbPalette
                       , labels=c("Sentinel Absent", "Sentinel Present")) +
  scale_x_discrete(labels=c("Commercial", "Green Area"))+
  theme(legend.position = 'bottom'
        , legend.title = element_blank()
        , axis.title.x = element_blank()
        , text=element_text(size = 12))
PeckPlot
```

@@

```{r Simple peck, include= F}
DATA.PECK<-DATA[complete.cases(DATA),]
DATA.PECK<-DATA.PECK[DATA.PECK$BEHAVIOR_PROPORTION!=0,]
LMM.Peck<-lmer(LPek~SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+BAIT_PRESENCE+(1|ID), data = DATA.PECK)
plot(LMM.Peck)
```

@@

```{r Bait effect on Peck Rate, echo = F}
BAITPlot.PECK<- DATA.PECK %>%
  summarySE(measurevar = "PECK_RATE"
            , groupvars = "BAIT_PRESENCE") %>%
  ggplot(aes(x = BAIT_PRESENCE, y = PECK_RATE))+
  geom_point(position = position_dodge(width = 0.9)
             , size = 3) +
  geom_text(aes(label = signif(PECK_RATE))
            , size = 3
            , position=position_dodge2(width=0.9, preserve='single')
            , hjust = -0.5
            , vjust = 0.1)+
  geom_errorbar(aes(ymin=(PECK_RATE-se), ymax=(PECK_RATE+se))
                , width = 0.2
                , position = position_dodge(width=.9))+
  theme_bw()+
  theme(text=element_text(size = 14))+
  xlab("Bait Presence")+
  ylab("Peck Rate in Pecks per minute")+
  theme(legend.position = 'bottom'
        )
BAITPlot.PECK
```

>>>>

```{r Open Crow and manage, include =F}
setwd(getwd())
Crow<-read.csv("Crow.csv", stringsAsFactors = T)
#Removing outliers
Crow<-Crow[which(Crow$Duration>0.01),]

#Some management #
Crow$ID<-as.factor(Crow$ID)
Crow$Number.of.Crows<-as.numeric(Crow$Number.of.Crows)
Crow$CODED_BAIT<-as.numeric(Crow$CODED_BAIT)
Crow$CODED_G.ENV<-as.numeric(Crow$CODED_G.ENV)
Crow$CODED_NB_CROWS<-as.numeric(Crow$CODED_NB_CROWS)
Crow$CODED_SENTINEL<-as.numeric(Crow$CODED_SENTINEL)
Crow$CODED_BEHAVIOR<-as.numeric(Crow$CODED_BEHAVIOR)
Crow$LDur<-log(Crow$Duration+1)
```

@@

```{r Dot Plot V2, echo = F}
source("./Calculate Summary Table with SE, SD, CI by grouping variables.R")
MeanDur <- summarySE(data = Crow, measurevar = "Duration"
                     , groupvars = c("G.Env", "Behavior", "Sentinel"))
DurDot<-ggplot(data = MeanDur
               , aes(x = Behavior
                     , y = Duration
                     , color = Behavior
                     , shape = Sentinel))+
  geom_point(position = position_dodge2(width = 0.9)
             , size = 3) +
  geom_errorbar(aes(ymin=(Duration-se)
                    , ymax=(Duration+se))
                , width = 0.2
                , position = position_dodge(width=0.9))+
  theme_classic() +
  ylab("Mean Bout Duration (s)") +
  scale_colour_manual(values = cbPalette
                      , guide="none") +
  scale_shape_manual(values = c(16,17)
                     , labels = c("Sentinel Absent"
                                  , "Sentinel Present")) +
  scale_x_discrete(labels = c("Foraging", "Alert", "Moving"))+
  theme(axis.title.x = element_blank()
        , legend.position = "bottom"
        , legend.box="vertical"
        , legend.margin=margin()) +
  facet_grid(~G.Env)

@@

<!-- ### PCAs -->
<!-- ```{r Bout Duration PCA packages, include=F} -->
<!-- library("FactoMineR") -->
<!-- library("factoextra") -->
<!-- ``` -->
<!-- ```{r Bout Duration PCA Book keeping, include=F} -->
<!-- PCA.Crow.Data<-Crow[,c(4,6,8,10,12:13)] -->
<!-- head(PCA.Crow.Data) -->
<!-- ``` -->
<!-- ```{r Bout Duration PCA, echo=F} -->
<!-- PCA.Crow<-PCA(PCA.Crow.Data[,-5], ncp=5) -->
<!-- ``` -->

<!-- >I'm new to PCAs, so bear with me please. From what I see, presence of bait and sentinel, and the number of crows all contibute to PC1, while Generalized environment seems to be contributing to PC2. The behavior appears to contribute to PC2, but not a lot. -->

<!-- #### Eigenvalues -->

<!-- >Let's have a look at the eigenvalues. -->

<!-- ``` {r Bout Duration PCA eigenvalues, echo = F} -->
<!-- Crow.eig.val<-get_eigenvalue(PCA.Crow) -->
<!-- Crow.eig.val -->
<!-- ``` -->

<!-- >Pretty small values. The second column shows how much contribution each dimension has to explain the total variance in the data. Let's quickly plot that. -->

<!-- #### Scree Plot -->

<!-- ```{r Bout Duration PCA Scree Plot, echo = F} -->
<!-- fviz_eig(PCA.Crow, addlabels=T, ylim = c(0,40)) -->
<!-- ``` -->

<!-- >Pretty cool. The first 3 PCs explain ~77% of the variance. Adding the 4th PC explains ~93% of the variation. -->

<!-- #### Contribution of variables to Principal Components -->

<!-- ```{r Bout Duration PCA var results, include = F} -->
<!-- Crow.var<-get_pca_var(PCA.Crow) -->
<!-- ``` -->
<!-- ```{r Bout Duration PCA Contribution Dim 1, echo=F} -->
<!-- fviz_contrib(PCA.Crow, choice="var", axes = 1, top = 20) -->
<!-- ``` -->

<!-- >The red dotted line represents the expected average contribution, assuming the contribution of the variables were uniform. In other words, the line is equal to 1/the number of variables; in this case 1/5 or 20%. -->

<!-- > From this plot, I can see that, as I saw previously in the correlation circle, the number of crows, the presence of a sentinel and the presence of bait contribute the most to PC1 (Dimension 1) -->

<!-- ```{r Bout Duration PCA Contribution Dim 2, echo=F} -->
<!-- fviz_contrib(PCA.Crow, choice="var", axes = 2, top = 20) -->
<!-- ``` -->

<!-- > The generalized environment contributes the most to PC2. -->

<!-- ```{r Bout Duration PCA Contribution Dim 3, echo=F} -->
<!-- fviz_contrib(PCA.Crow, choice="var", axes = 3, top = 20) -->
<!-- ``` -->

<!-- >The coded behavior contributes most to PC3. -->

<!-- ```{r Bout Duration PCA Contribution Dim 4, echo=F} -->
<!-- fviz_contrib(PCA.Crow, choice="var", axes = 4, top = 20) -->
<!-- ``` -->

<!-- >OK! Now we're getting to the interesting bits. The presence of bait and the presence of a Sentinel contribute most to PC4. This makes me curious to see if there is an interaction between the two factors. -->

<!-- ```{r Bout Duration PCA Contribution Dim 5, echo=F} -->
<!-- fviz_contrib(PCA.Crow, choice="var", axes = 5, top = 20) -->
<!-- ``` -->

<!-- >>The presence of a sentinel and the size of the group contribute most to PC 5. I believe this would imply that the interaction between the two could be interesting to look at. Considering these two variables are also major contributors to PC1, this makes the inclusion of the interaction in the model a must. -->

<!-- >From this, I believe I should look at the interaction between NB_Crows, Presence of a sentinel, and the presence of bait. -->

<!-- #### Plotting with Behaviors -->

<!-- >I'd like to plot the dimensions using the behaviors of the bouts. -->

<!-- ```{r Bout Duration PCA Plot with Behavior PC1-2, echo=F} -->
<!-- fviz_pca_ind(PCA.Crow -->
<!--              , geom.ind="point" -->
<!--              , col.ind=PCA.Crow.Data$Behavior -->
<!--              , palette = cbPalette -->
<!--              , addEllipses = T -->
<!--              , legend.title = "Behaviors" -->
<!--              ) -->
<!-- ``` -->

<!-- >Messy. The mean points of the behaviors are relatively centered. -->

<!-- ```{r Bout Duration PCA Plot with Behavior PC2-3, echo=F} -->
<!-- fviz_pca_ind(PCA.Crow -->
<!--              , axes = c(2,3) -->
<!--              , geom.ind="point" -->
<!--              , col.ind=PCA.Crow.Data$Behavior -->
<!--              , palette = cbPalette -->
<!--              , addEllipses = T -->
<!--              , legend.title = "Behaviors" -->
<!--              ) -->
<!-- ``` -->

<!-- >Very clear separation by behavior type, with 'Head Up' shifted upward, 'Head Down' shifted downward, and 'Moving' in the middle. -->

<!-- ```{r Bout Duration PCA Plot with Behavior PC1-3, echo=F} -->
<!-- fviz_pca_ind(PCA.Crow -->
<!--              , axes = c(1,3) -->
<!--              , geom.ind="point" -->
<!--              , col.ind=PCA.Crow.Data$Behavior -->
<!--              , palette = cbPalette -->
<!--              , addEllipses = T -->
<!--              , legend.title = "Behaviors" -->
<!--              ) -->
<!-- ``` -->

<!-- >Good separation, but the concentration ellipses have increased in size. Curious. -->

<!-- #### Biplot -->

<!-- >Finally, let's look at the biplot. From what I understand, it is essentially the correlation circle overlaid onto the data. -->

<!-- ```{r Bout Duration PCA Biplot PC1-2, echo=F} -->
<!-- fviz_pca_biplot(PCA.Crow -->
<!--                 ,geom.ind = "point" -->
<!--                 , repel = T -->
<!--                 , col.ind=PCA.Crow.Data$Behavior -->
<!--                 , addEllipses = T -->
<!--                 , label = "var" -->
<!--                 , palette=cbPalette -->
<!--                 , col.var="black" -->
<!--                 , legend.title = "Behavior") -->
<!-- ``` -->
<!-- ```{r Bout Duration PCA Biplot PC2-3, echo=F} -->
<!-- fviz_pca_biplot(PCA.Crow -->
<!--                 , axes = c(2,3) -->
<!--                 , geom.ind = "point" -->
<!--                 , repel = T -->
<!--                 , col.ind=PCA.Crow.Data$Behavior -->
<!--                 , addEllipses = T -->
<!--                 , label = "var" -->
<!--                 , palette=cbPalette -->
<!--                 , col.var="black" -->
<!--                 , legend.title = "Behavior") -->
<!-- ``` -->
<!-- ```{r Bout Duration PCA Biplot PC1-3, echo=F} -->
<!-- fviz_pca_biplot(PCA.Crow -->
<!--                 , axes = c(1,3) -->
<!--                 , geom.ind = "point" -->
<!--                 , repel = T -->
<!--                 , col.ind=PCA.Crow.Data$Behavior -->
<!--                 , addEllipses = T -->
<!--                 , label = "var" -->
<!--                 , palette=cbPalette -->
<!--                 , col.var="black" -->
<!--                 , legend.title = "Behavior") -->
<!-- ``` -->

<!-- >Nice! I think I've done the PCA analysis to the best of my abilities, but I am very much open to comments and feedback! -->

<!-- >From what I can gather, I should model the data as follows:/ -->
<!-- >LDur~Behavior+NB_Crows*Bait*Sentinel+G.Env+(1|ID) -->

@@

```{r Duration RLMM, echo=F}
RLMM.Dur.I<-rlmer(LDur~Behavior+Sentinel*G.Env+Sentinel*CODED_NB_CROWS+Baited+Sentinel+G.Env+ (1|ID), data = Crow)
plot(RLMM.Dur.I)
```

@@

```{r Duration Better Summary, echo = F}
sjPlot::tab_model(RLMM.Dur.I
                  , show.re.var = T
                  , title = "Model Results with Interactions"
                  , dv.labels = " Effects of on duration of behaviors"
                  , file="Tab_Dur_Model.html")

@@

```{r Effect Sizes}
sjPlot::plot_model(RLMM.Dur.I
                   , show.values=T
                   , show.p=T
                   , value.offset = 0.4
                   , value.size = 3.5
                   , wrap.title = 48
                   , title = "Effects of environment, presence of a sentinel, number of crows and bait on durations of behaviors")# Looks much better
```
>Let's try the good old regular lmer and see if that changes anything.

@@

```{r Bait effect on HD bout, echo = F}
BaitPlot<- Crow[which(Crow$Behavior=="HD"),] %>%
  summarySE(measurevar = "Duration"
            , groupvars = "Baited") %>%
  ggplot(aes(x = Baited, y = Duration))+
  geom_point(position = position_dodge(width = 0.9)
             , size = 3) +
  geom_errorbar(aes(ymin=(Duration-se), ymax=(Duration+se))
                , width = 0.1
                , position = position_dodge(width=.9))+
  theme_classic()+
  theme(text=element_text(size = 14))+
  xlab("")+
  ylab("Mean Bout Duration (s)")+
  scale_x_discrete(labels=c("Not Baited", "Baited"))+
  theme(legend.position = 'none'
        )
BaitPlot
```

@@

```{r Proportion Barplot, echo = F}
Prop<-ggplot(MeanProp, aes(x = SENTINEL_PRESENCE, y = BEHAVIOR_PROPORTION, fill = BEHAVIOR))+
  geom_bar(stat = 'identity', position = 'stack')+
  geom_text(aes(label = paste0(formattable::digits(BEHAVIOR_PROPORTION*100, dig=2), "%"))
            , position = position_stack(vjust = 0.5)
            , size = 3) +
  scale_y_continuous(labels = scales::percent) +
  theme_classic()+
  theme(text=element_text(size = 10)
        , axis.title.x = element_blank())+
  ylab("Proportion of time")+
  scale_x_discrete(labels=c("Sentinel Absent", "Sentinel Present"))+
  scale_fill_manual(values = cbPalette, labels = c("Foraging", "Alert", "Moving"), name="Behavior")+
  theme(legend.position = "bottom")+
  facet_grid(~GENERALIZED_ENVIRONMENT)
Prop
```

@@

```{r Peck Per Minute Histograms Individual, include = F}
Untransformed.PPM<-hist(DATA$PECK_RATE, na.rm=T, breaks = 25)
Transformed.PPM<-hist(DATA$LPek, breaks = 25)
```

@@

```{r Peck Plots, echo = F}
PeckPlot<-ggplot(MeanPeck, aes(x = SENTINEL_PRESENCE, y = PECK_RATE, color=SENTINEL_PRESENCE))+
  geom_point(position = position_dodge(width = 0.9)
             , size = 3)+
  # geom_text(aes(label = signif(PECK_RATE))
  #           , size = 3
  #           , position=position_dodge2(width=1, preserve='single')
  #           , hjust = -0.5
  #           , vjust = 0.1)+
  geom_errorbar(aes(ymin=(PECK_RATE-se), ymax=(PECK_RATE+se))
                , width = 0.1
                , position = position_dodge(.9))+
  theme_classic()+
  labs(colour = "Presence of a sentinel")+
  ylab("Mean pecks per minute")+
  scale_color_manual(values = cbPalette
                       , labels=c("Sentinel Absent", "Sentinel Present")) +
  scale_x_discrete(labels=c("Sentinel Absent", "Sentinel Present"))+
  theme(legend.position = ''
        , legend.title = element_blank()
        , axis.title.x = element_blank()
        , text=element_text(size = 12)) +
  facet_grid(~GENERALIZED_ENVIRONMENT)
PeckPlot
```

@@

```{r Simple peck, include= F}
DATA.PECK<-DATA[complete.cases(DATA),]
DATA.PECK<-DATA.PECK[DATA.PECK$BEHAVIOR_PROPORTION!=0,]
LMM.Peck<-lmer(LPek~SENTINEL_PRESENCE*GENERALIZED_ENVIRONMENT+BAIT_PRESENCE+(1|ID), data = DATA.PECK)
plot(residuals(LMM.Peck))
```

@@

```{r Bait effect on Peck Rate, echo = F}
BAITPlot.PECK<- DATA.PECK %>%
  summarySE(measurevar = "PECK_RATE"
            , groupvars = "BAIT_PRESENCE") %>%
  ggplot(aes(x = BAIT_PRESENCE, y = PECK_RATE))+
  geom_point(position = position_dodge(width = 0.9)
             , size = 3) +
  # geom_text(aes(label = signif(PECK_RATE))
  #           , size = 3
  #           , position=position_dodge2(width=0.9, preserve='single')
  #           , hjust = -0.5
  #           , vjust = 0.1)+
  geom_errorbar(aes(ymin=(PECK_RATE-se), ymax=(PECK_RATE+se))
                , width = 0.1
                , position = position_dodge(width=.9))+
  theme_classic()+
  theme(text=element_text(size = 14))+
  xlab("Bait Presence")+
  ylab("Peck Rate in Pecks per minute")+
  theme(legend.position = 'bottom'
        )
BAITPlot.PECK
```
